

```{r include=FALSE}
#outputFile <- "report-copy.pdf"
render_markdown()
opts_chunk$set(fig.path='./figs/',tidy=TRUE)
opts_knit$set(concordance=TRUE)
```

# 
## Author: A. Blejec



```{r Author:,echo=FALSE}
###############################################
##                                           ##
## (c) Andrej Blejec (andrej.blejec@nib.si)  ##
##                                           ##
###############################################
```
```{r initialize,echo=FALSE,results='hide',message=FALSE}
options(width=70)
#library(Hmisc)
#library(xlsReadWrite)
```

## 

```{r }

```




## SessionInfo
{
```{r sessionInfo,results='asis',echo=FALSE}
cat(win.version(),"\n")
sessionInfo()
sdir <- gsub("/","/\\\n ",dirname(getwd()))
#cat("Project path:\n`",sdir,"`\\\\\n")
cat("Project path:\n",sdir,"\\\\\n")
args <- commandArgs(trailingOnly = TRUE)
mainFile <- basename(args[1])
#
mainFilePath <- file.path("../doc", mainFile)
mainFilePath <- gsub("/./","/",mainFilePath)
cat("Main file :`", mainFilePath, "`\n")
#

mainFile <- strsplit(mainFile,'.',fixed=TRUE)[[1]][1]
projectName <- rev((strsplit(dirname(getwd()), "/"))[[1]])[1]
#
```

### View as vignette
Project files can be viewed by pasting this code to \R\ console:
```{r projectFiles,echo=FALSE,results='asis'}
cat('projectName <-"',projectName,'"; ',sep="")
cat(' mainFile <-"',mainFile,'"',sep="")
#
```{r vignette,echo=FALSE,results='asis'}
cat(
' commandArgs()\n',
'library(tkWidgets)\n',
'openPDF(file.path(dirname(getwd()),"doc",\n',
'paste(mainFile,"PDF",sep=".")))\n',
'viewVignette("viewVignette", projectName,\n',
'file.path("../doc",paste(mainFile,"Rnw",sep=".")))\n'
)
#
```

`Git Revision: \gitCommitterUnixDate \gitAbbrevHash{` (\gitCommitterDate)} \hfill \copyright A. Blejec
` \gitReferences` \hfill \verb'`r mainFilePath`'

}

```{r eval=FALSE,echo=FALSE}
# getrootpath <- function() {
# fp <- (strsplit(getwd(), "/"))[[1]]
# file <- file.path(paste(fp[-length(fp)], collapse = "/"))
# return(file)
# }
# fileName <- function(name="bla",ext="PDF") paste(name,ext,sep=".")
```


